The Atala PRISM Protocol

### 2022-12-21 prism-backend/research/prism-protocol/did_atala.tex
.

\subsubsection{Notes for Implementations.} %

We acknowledge that, in the pseudocode given in \figref{fig:atalapkidid1} and
\figref{fig:atalapkidid2}, we have favoured notational simplicity over
implementation efficiency or
convenience. For instance, it is not really needed that the master key signing a
transaction is the one with the lowest index -- any such key can actually do it.
However, it makes notation much easier. Similarly, in practice it may be easier
to use different ``function arguments'' to denote the set of keys to remove and
a set of keys to add from/to an existing DID. However, notationally it is
simpler to follow the chosen (equivalent) approach. Finally, key indexes don't
need to follow a sequential order.

@@

@@

\begin{lemma}[Mergeability of \gAtala]
  \label{lma:gAtala}

@@

\begin{proof}
  \todo{In the sequel, when the $\gamma_i$'s should be protocols, not ideal
    functionalities; e.g., $\gamma_3 = \IdealP_{\IdealGclock}$, not
    $\IdealGclock$ (the argument should be ok, it is just a wording error).}
  We start with the first item, for which we briefly recall the notion of
  subroutine respecting protocols. Intuitively, a protocol $\pi$ is subroutine
  respecting if, for any session \sid of $\pi$, the main parties of \sid are the
  only ones that communicate with the outside world; this also means that
  subparties only accept input and subroutine output from parties in \sid. A
  more precise definition is available in the 2020 version of \cite{canetti00}.

@@

  In summary, $\gamma_3 = \IdealGclock$ and $\gamma_2 = \IdealGRO$ are
  subroutine respecting (and, obviously, $\gamma_2$ is also subroutine
  respecting except for calls to $\gamma_3$). Also, $\gamma_1 = \IdealGdledger$
  is subroutine respecting except for calls to $\gamma_3$ -- and, since
  $\gamma_1$ does not use $\gamma_2$, it is trivially also subroutine respecting
  except for calls to $\gamma_2$ and $\gamma_3$.

  Thus, condition 1 of \lmaref{lma:gAtala} is met. Now, we move to condition 2.

  \qed
\end{proof}

>>>>

\subsubsection{Notes for Implementations.} %
\todo{This needs updating. However, keeping it here until I confirm.}
We acknowledge that, in the pseudocode given in \figref{fig:atalapkidid1} and
\figref{fig:atalapkidid2}, we have favoured notational simplicity over
implementation efficiency or
convenience. For instance, it is not really needed that the master key signing a
transaction is the one with the lowest index -- any such key can actually do it.
However, it makes notation much easier. Similarly, in practice it may be easier
to use different ``function arguments'' to denote the set of keys to remove and
a set of keys to add from/to an existing DID. However, notationally it is
simpler to follow the chosen (equivalent) approach. Finally, key indexes don't
need to follow a sequential order.

@@

\commentwho{Jesus}{What follows is essentially right on its own, but I interpreted
  \cite{bhz21} somehow wrongly. The approach is: (1) merge all (ideal) global
  subroutines (ledger, RO, clock) into one (\gAtala); (2) prove that theorem 1
  below is met, where the real protocol is \RealPKIDIDAtala, and the ideal
  (global) functionality is \IdealGPKIDID -- although we can ignore that it is
  a global functionality here. Then, it would be nice to prove that Cardano as
  instantiation of the ledger, and whatever else for RO and clock, allow to
  instantiate the merged global subroutine (this is what I've mostly done next,
  to some extent). So, basically, revert the order of what I was trying to do.}

@@

\begin{lemma}[Mergeability of \gAtala \todo{``Mergeability'' may not be the
    best term}]
  \label{lma:gAtala}

  % Let $\gamma_1 \gets \IdealGPKIDID$, $\gamma_2 \gets \IdealGdledger$,
  % $\gamma_3 \gets \IdealGRO$, $\gamma_4 \gets \IdealGclock$. Then:

@@

\begin{proof}
  We start with the first item, for which we briefly recall the notion of
  subroutine respecting protocols. Intuitively, a protocol $\pi$ is subroutine
  respecting if, for any session \sid of $\pi$, the main parties of \sid are the
  only ones that communicate with the outside world; this also means that
  subparties only accept input and subroutine output from parties in \sid. A
  more precise definition is available in the 2020 version of \cite{canetti00}.

@@

  % The same argument as for \IdealGdledger applies for \IdealGPKIDID, since it
  % also leverages \IdealGclock ($\gamma_4$) in its definition.

  In summary, $\gamma_3 = \IdealGclock$ and $\gamma_2 = \IdealGRO$ are
  subroutine respecting (and, obviously, $\gamma_2$ is also subroutine
  respecting except for calls to $\gamma_3$). Also, $\gamma_1 = \IdealGdledger$
  is subroutine respecting except for calls to $\gamma_3$ -- and, since
  $\gamma_1$ does not use $\gamma_2$, it is trivially also subroutine respecting
  except for calls to $\gamma_2$.

  Thus, condition 1 of \lmaref{lma:gAtala} is met, except for the subroutine
  exposing part. However, even though it is not explicitly stated in their
  corresponding definitions, it is possible to transform the \IdealGclock,
  \IdealGRO and \IdealGdledger (by adding a directory ITI and an extra shell
  taking care of the proper redirections) so that they are actually subroutine
  exposing - cf \cite[Definition 2.7]{bch+20}. Now, we move to condition 2.
  Concretely:

  \begin{itemize}
  \item $\gamma_2$ is $\gamma_1$-regular: The main (dummy) parties in
    $\gamma_2$ ($\IdealP_{\IdealGRO}$) do not invoke new ITIs of $\gamma_1$
    ($\IdealP_{\IdealGdledger}$) via messages to the subroutine output tape.
    Also, the main (dummy) parties of $\IdealP_{\IdealGRO}$ do not have an ITI
    with code $\IdealP_{\IdealGdledger}$ as subsidiary.
  \item $\gamma_3$ is $\gamma_2$-regular: The main (dummy) parties in
    $\gamma_3$ ($\IdealP_{\IdealGclock}$) do not invoke new ITIs of $\gamma_2$
    ($\IdealP_{\IdealGRO}$) via messages to the subroutine output tape. Also,
    the main (dummy) parties of $\IdealP_{\IdealGclock}$ do not have an ITI with
    code $\IdealP_{\IdealGRO}$ as subsidiary.
  \item $\gamma_3$ is $\gamma_1$-regular: The main (dummy) parties in
    $\gamma_3$ ($\IdealP_{\IdealGclock}$) do not invoke new ITIs of $\gamma_1$
    ($\IdealP_{\IdealGdledger}$) via messages to the subroutine output tape --
    dummy parties in $\gamma_3$ pass subroutine output to parties in $\gamma_1$,
    but already existing ones. Also, the main (dummy) parties of
    $\IdealP_{\IdealGclock}$ do not have an ITI with code
    $\IdealP_{\IdealGdledger}$ as subsidiary.
  \end{itemize}
  %
  \qed
\end{proof}
